GEE models

### 2017-07-11 doc/manuscript.Rmd
s/pct/chg

For this study, there were 
`r female$npct` females and `r european$npct` had European-ancestry (see 
`r cite_t("basic")`). The mean follow-up time was `r calc_followup_time()`
years, where `r calc_pct_full_visits()`% of participants attended all three
visits.
The average age of the participants was `r aide::average(ds0yr$Age)` years 
(`r aide::stddev(ds0yr$Age)` SD) and the average BMI was
`r aide::average(ds0yr$BMI)` (`r aide::stddev(ds0yr$BMI)` SD). Most of the 
participants, `r famhist$npct`, had a family history of diabetes.
Insulin sensitivity and beta-cell function measures showed a significant median
decline between
`r pct_outcomes$chg` (p`r pct_outcomes$p`) over the 6
years in this analysis of the PROMISE cohort.
Consistent with this decline, there were `r calc_incid_dysgly("ConvertDM")`
and `r calc_incid_dysgly("ConvertPreDM")`incident cases of diabetes and pre-diabetes (IFG and IGT),
respectively, over the 6-years. Incident diabetes cases were excluded from further GEE
analyses.

>>>>

For this study, there were 
`r female$npct` females and `r european$npct` had European-ancestry (see 
`r cite_t("basic")`). The mean follow-up time was `r calc_followup_time()`
years, where `r calc_pct_full_visits()`% of participants attended all three
visits.
The average age of the participants was `r aide::average(ds0yr$Age)` years 
(`r aide::stddev(ds0yr$Age)` SD) and the average BMI was
`r aide::average(ds0yr$BMI)` (`r aide::stddev(ds0yr$BMI)` SD). Most of the 
participants, `r famhist$npct`, had a family history of diabetes.
Insulin sensitivity and beta-cell function measures showed a significant median
decline between
`r chg_outcomes$chg` (p`r chg_outcomes$p`) over the 6
years in this analysis of the PROMISE cohort.
Consistent with this decline, there were `r calc_incid_dysgly("ConvertDM")`
and `r calc_incid_dysgly("ConvertPreDM")`incident cases of diabetes and pre-diabetes (IFG and IGT),
respectively, over the 6-years. Incident diabetes cases were excluded from further GEE
analyses.
